A parametricity-based formalization of semi-simplicial and semi-cubical sets

### 2023-01-21 paper/paper.tex
referring to Yoneda embedding since this seems very standard terminology

\begin{definition}[$\DeltaPlus^n$]
  The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as:

@@

\begin{definition}[$\Cube^n$]
  The standard semi-cube $\Cube^n$ is defined as:

>>>>

\begin{definition}[$\DeltaPlus^n$]
  The standard augmented $n$-semi-simplex $\DeltaPlus^n$ is defined as what is called the Yoneda embedding of $n\in\Obj(\DeltaPlus)$:

@@

\begin{definition}[$\Cube^n$]
  The standard semi-cube $\Cube^n$ is defined as the Yoneda embedding of $n\in\Obj(\Cube)$:
